---
title: "Redface Blackface Study-replicating a paper draft"
author: "Ari"
date: "6/13/2019"
output: 
  html_document:
    toc: True
    toc_depth: 5
    toc_float: 
      collapsed: False
    number_sections: True
    code_folding: hide
  
---

## Necessary Packages
```{r load packages}
library(psych) # For reverse coding variables and reading data files
library(multicon) # For creating composites
library(tidyverse)
library(haven)
library(labelled)
```

## Functions to center things 
```{r functions}

center<-function(MOD)
{
  centered<-MOD-mean(MOD,na.rm=TRUE)
  return(centered)
}

low<-function(MOD)
{
  low<-(MOD-mean(MOD,na.rm=TRUE))+sd(MOD, na.rm=TRUE)
  return(low)
}

high<-function(MOD)
{
  high<-(MOD-mean(MOD, na.rm=TRUE))-sd(MOD, na.rm=TRUE)
  return(high)
}

gmc <- function(MOD, grp) 
  { 
  gmcentered<- (MOD-tapply(MOD,grp,mean,na.rm=TRUE)[grp])
  return(gmcentered)

}

```

## Prepping Data File
```{r Read Data File}
BFRF1 <- read_sav("/Users/arianneeason/Downloads/Paper_Study1.sav", user_na = FALSE)
#BFRF1 <- subset(BFRF1, V10==1)
BFRF1 <- subset(BFRF1, Race==3)
```

Blackface Composite All Items
```{r BF Composite All Items}

BFRF1_Blackface.All <- 
 BFRF1 %>% 
  select(
    BFPaint1_1,
    BFPaint1_2,
    BFPaint1_3,
    BFPaint1_4,
    BFPaintWom1_1,
    BFPaintWom1_2,
    BFPaintWom1_3,
    BFPaintWom1_4, 
    BFGroup1_1, 
    BFGroup1_2,
    BFGroup1_3,
    BFGroup1_4, 
    BFPaintMan2_1, 
    BFPaintMan2_2, 
    BFPaintMan2_3, 
    BFPaintMan2_4, 
    BFPaintWom2_1,
    BFPaintWom2_2,
    BFPaintWom2_3,
    BFPaintWom2_4, 
    BFGroup2_1, 
    BFGroup2_2, 
    BFGroup2_3, 
    BFGroup2_4
  )

BF.All.Key = c(1, -1, 1, -1, 
           1, -1, 1, -1,
           1, -1, 1, -1,
           1, -1, 1, -1,
           1, -1, 1, -1,
           1, -1, 1, -1) #Reverse Scoring Items

BFRF1_Blackface.All.data <-
  reverse.code(BF.All.Key,
               BFRF1_Blackface.All,
               mini = 1,
               maxi = 7)

BF.All.comp <-
  multicon::composite(BFRF1_Blackface.All.data,
  rel = TRUE, 
  nomiss = 0.6) # Making Composite

BF.All <- as.data.frame(BF.All.comp)
```

Blackface Compsite sans One Photo
```{r BF Composite Sans One Item}

BFRF1_Blackface <- 
 BFRF1 %>% 
  select(
    BFPaint1_1,
    BFPaint1_2,
    BFPaint1_3,
    BFPaint1_4,
    BFPaintWom1_1,
    BFPaintWom1_2,
    BFPaintWom1_3,
    BFPaintWom1_4, 
    BFGroup1_1, 
    BFGroup1_2,
    BFGroup1_3,
    BFGroup1_4, 
    BFPaintMan2_1, 
    BFPaintMan2_2, 
    BFPaintMan2_3, 
    BFPaintMan2_4, 
    #BFPaintWom2_1,
    #BFPaintWom2_2,
    #BFPaintWom2_3,
    #BFPaintWom2_4, 
    BFGroup2_1, 
    BFGroup2_2, 
    BFGroup2_3, 
    BFGroup2_4
  )

BF.Key = c(1, -1, 1, -1, 
           1, -1, 1, -1,
           1, -1, 1, -1,
           1, -1, 1, -1,
           #1, -1, 1, -1,
           1, -1, 1, -1) #Reverse Scoring Items
BFRF1_Blackface.data <-
  reverse.code(BF.Key,
               BFRF1_Blackface,
               mini = 1,
               maxi = 7)

BF.comp <-
  multicon::composite(BFRF1_Blackface.data,
  rel = TRUE, 
  nomiss = 0) # Making Composite

BF <- as.data.frame(BF.comp)
```

Redface Composite
```{r RF Composite All Items}

BFRF1_Redface.All <- 
 BFRF1 %>% 
  select(
    RFPaintGroup2_1,
    RFPaintGroup2_2,
    RFPaintGroup2_3,
    RFPaintGroup2_4,
    RFPaintWom1_1,
    RFPaintWom1_2,
    RFPaintWom1_3,
    RFPaintWom1_4,
    RFPaintGroup1_1,
    RFPaintGroup1_2,
    RFPaintGroup1_3,
    RFPaintGroup1_4,
    RFPaintMan2_1,
    RFPaintMan2_2,
    RFPaintMan2_3,
    RFPaintMan2_4,
    RFPaintWom2_1,
    RFPaintWom2_2,
    RFPaintWom2_3,
    RFPaintWom2_4,
    RFGroup2_1,
    RFGroup2_2, 
    RFGroup2_3, 
    RFGroup2_4
  )

RF.All.Key = c(1, -1, 1, -1, 
           1, -1, 1, -1,
           1, -1, 1, -1,
           1, -1, 1, -1,
           1, -1, 1, -1,
           1, -1, 1, -1) #Reverse Scoring Items
BFRF1_Redface.All.data <-
  reverse.code(RF.All.Key,
               BFRF1_Redface.All,
               mini = 1,
               maxi = 7)

RF.All.comp <-
  multicon::composite(BFRF1_Redface.All.data,
  rel = TRUE, 
  nomiss = 0) # Making Composite

RF.All <- as.data.frame(RF.All.comp)
```

Redface Composite Sans One Photo
```{r RF Composite Sans one Item}

BFRF1_Redface <- 
 BFRF1 %>% 
  select(
    RFPaintGroup2_1,
    RFPaintGroup2_2,
    RFPaintGroup2_3,
    RFPaintGroup2_4,
    RFPaintWom1_1,
    RFPaintWom1_2,
    RFPaintWom1_3,
    RFPaintWom1_4,
    RFPaintGroup1_1,
    RFPaintGroup1_2,
    RFPaintGroup1_3,
    RFPaintGroup1_4,
    RFPaintMan2_1,
    RFPaintMan2_2,
    RFPaintMan2_3,
    RFPaintMan2_4,
    #RFPaintWom2_1,
    #RFPaintWom2_2,
    #RFPaintWom2_3,
    #RFPaintWom2_4,
    RFGroup2_1,
    RFGroup2_2, 
    RFGroup2_3, 
    RFGroup2_4
  )

RF.Key = c(1, -1, 1, -1, 
           1, -1, 1, -1,
           1, -1, 1, -1,
           1, -1, 1, -1,
           #1, -1, 1, -1,
           1, -1, 1, -1) #Reverse Scoring Items
BFRF1_Redface.data <-
  reverse.code(RF.Key,
               BFRF1_Redface,
               mini = 1,
               maxi = 7)

RF.comp <-
  multicon::composite(BFRF1_Redface.data,
  rel = TRUE, 
  nomiss = 0) # Making Composite

RF <- as.data.frame(RF.comp)
```

Racism Minimization-Black
```{r Black Racism Minimization Composite}
BFRF1_BlackRaceMini <- 
 BFRF1 %>% 
  select(RacismMini_1,
         RacismMini_2,
         RacismMini_3,
         RacismMini_4,
         RacismMini_5,
         RacismMini_6,
         RacismMini_7,
         RacismMini_8, 
         RacismMini_9,
         RacismMini_10
  )

RacismMini.Key = c(1, -1, 1, -1, -1,
                   -1, -1, 1, 1, 1) #Reverse Scoring Items
BFRF1_BlackRaceMini.data <-
  reverse.code(RacismMini.Key,
               BFRF1_BlackRaceMini,
               mini = 1,
               maxi = 7)

BlackRaceMini.comp <-
  multicon::composite(BFRF1_BlackRaceMini.data,
  rel = TRUE, 
  nomiss = 0) # Making Composite

BlkMini <- as.data.frame(BlackRaceMini.comp)


```

Racism Minimization Native
```{r Native Racism Minimization Composite}
BFRF1_NativeRaceMini <- 
 BFRF1 %>% 
  select(RacismMini_1.0,
         RacismMini_2.0,
         RacismMini_3.0,
         RacismMini_4.0,
         RacismMini_5.0,
         RacismMini_6.0,
         RacismMini_7.0,
         RacismMini_8.0, 
         RacismMini_9.0,
         RacismMini_10.0
  )

RacismMini.Key = c(1, -1, 1, -1, -1,
                   -1, -1, 1, 1, 1) #Reverse Scoring Items
BFRF1_NativeRaceMini.data <-
  reverse.code(RacismMini.Key,
               BFRF1_NativeRaceMini,
               mini = 1,
               maxi = 7)

NativeRaceMini.comp <-
  multicon::composite(BFRF1_NativeRaceMini.data,
  rel = TRUE, 
  nomiss = 0) # Making Composite

NtvMini <- as.data.frame(NativeRaceMini.comp)


```

Adding Composites to File
```{r Adding Composites to Data File}
BFRF1 <- cbind(BFRF1, RF, BF, BF.All, RF.All, BlkMini, NtvMini)
```

Creating New Variables
Acceptability.Check variable should be the same as the OK variable
```{r Combining Columns}
#One column with racism minimization values
BFRF1 <- BFRF1 %>% 
  mutate(RaceMini = coalesce(NativeRaceMini.comp, BlackRaceMini.comp)) 

#One column with acceptability ratings
BFRF1 <- BFRF1 %>% 
  mutate(Acceptability = coalesce(RF.comp, BF.comp)) 

#One column with acceptability.all ratings
BFRF1 <- BFRF1 %>% 
  mutate(Acceptability.AllPhotos = coalesce(RF.All.comp, BF.All.comp)) 

#One column with acceptability.checking to align with prior analyses
BFRF1 <- BFRF1 %>% 
  mutate(Acceptability.Check = coalesce(RF.All.comp, BF.comp)) 
```

Coding Condition
```{r Recode Condition}
BFRF1 <- BFRF1 %>% 
  mutate(ConditionAri = Condition)

BFRF1 <- BFRF1 %>% 
  mutate(ConditionEffect = recode(ConditionAri, "0"=-1, "1"=1))

BFRF1 <- BFRF1 %>% 
  mutate(Blk0 = recode(ConditionAri, "0"=0, "1"=1))

BFRF1 <- BFRF1 %>% 
  mutate(Ntv0 = recode(ConditionAri, "0"=1, "1"=0))
```

## Analyses{.tabset}

### Main Effects 
```{r Main Effects }
M1 <- lm(Acceptability ~ 1 + ConditionEffect , data = BFRF1 )
summary(M1)

M1.1 <- lm(Acceptability.AllPhotos ~ 1 + ConditionEffect , data = BFRF1 )
summary(M1.1)

M1.2 <- lm(Acceptability.Check ~ 1 + ConditionEffect , data = BFRF1 )
summary(M1.2)

M1.3 <- lm(OK ~ 1 + ConditionEffect , data = BFRF1 )
summary(M1.3)
```

### Moderation
```{r Moderation}

R1 <- lm(Acceptability ~ 1 + center(RaceMini) + ConditionEffect + center(RaceMini)*ConditionEffect, data = BFRF1)
summary(R1)

R1.1 <- lm(Acceptability.AllPhotos ~ 1 + center(RaceMini) + ConditionEffect + center(RaceMini)*ConditionEffect, data = BFRF1)
summary(R1.1)

R1.2 <- lm(Acceptability.Check ~ 1 + center(RaceMini) + ConditionEffect + center(RaceMini)*ConditionEffect, data = BFRF1)
summary(R1.2)

R1.3 <- lm(OK ~ 1 + center(RaceMini) + ConditionEffect + center(RaceMini)*ConditionEffect, data = BFRF1)
summary(R1.3)

```


### Simple Slopes {.tabset}
#### Black Simple Slopes
```{r Black Simple Slopes Study 3 }
B1 <- lm(Acceptability ~ 1 + center(RaceMini) + Blk0 + center(RaceMini)*Blk0, data = BFRF1)
summary(B1)

B1.1 <- lm(Acceptability.AllPhotos ~ 1 + center(RaceMini) + Blk0 + center(RaceMini)*Blk0, data = BFRF1)
summary(B1.1)

B1.2 <- lm(Acceptability.Check ~ 1 + center(RaceMini) + Blk0 + center(RaceMini)*Blk0, data = BFRF1)
summary(B1.2)

B1.3 <- lm(OK ~ 1 + center(RaceMini) + Blk0 + center(RaceMini)*Blk0, data = BFRF1)
summary(B1.3)


```
#### Native Simple Slopes
```{r Native Simple Slopes Study 3 }
N1 <- lm(Acceptability ~ 1 + center(RaceMini) + Ntv0 + center(RaceMini)*Ntv0, data = BFRF1)
summary(N1)

N1.1 <- lm(Acceptability.AllPhotos ~ 1 + center(RaceMini) + Ntv0 + center(RaceMini)*Ntv0, data = BFRF1)
summary(N1.1)

N1.2 <- lm(Acceptability.Check ~ 1 + center(RaceMini) + Ntv0 + center(RaceMini)*Ntv0, data = BFRF1)
summary(N1.2)

N1.3 <- lm(OK ~ 1 + center(RaceMini) + Ntv0 + center(RaceMini)*Ntv0, data = BFRF1)
summary(N1.3)
```